---
title: "SCHAEFER"
author: "Miriam Schaefer"
format: 
  html:
    echo: false 
    warning: false
---

Find my github repository for this lab [here](https://github.com/miriam-schaefer/bt_empire).


```{r}
here::i_am("bt_empire.Rproj")
library(here)
library(vroom)
library(dplyr)
library(tidyr)
library(ggplot2)
```

## Question 3

```{r}
data <- vroom(here("datasets", "data%systems.csv"))
```

```{r}
summary(data)
```

## Question 4 
Describe the data set with a properly formatted table (either using kable or via a markdown table) according to the following metrics:

number of observations (i.e. star systems)
• number of variables
• number of missing values for each variable with missing values 
• number of observations with at least one missing value


```{r}
No_observations <- nrow(data) 
No_variables <- ncol(data) 
No_NA <- colSums(is.na(data)) 
Obs_with_NA <- sum(rowSums(is.na(data))>0) 

q4_table <- data.frame(
  Metric = c("Number of Observations", "Number of Variables", "Missing Values per Variable", "Observations with Missing Values"),
  Value = c(No_observations, No_variables, paste(No_NA, collapse = ", "), Obs_with_NA)
)

knitr::kable((q4_table), "simple") 
```




## Question 5
*Represent graphically the luminosity of a star as a function of its temperature. Make sure to get rid of any warning or error!*

```{r}
q5 <- data |> 
  na.omit() |>
  ggplot(aes(x=`effective temperature`, y=`Luminosity`)) + 
  geom_point()

q5
```


## Question 6
Report in a table the most extreme stars with respect to the numerical variables. This should include, for instance, the most and least massive stars. Do that variable by variable.

```{r}
# Distance 
min_dist <- min(data$`DISTANCE (LIGHTYEARS)`, na.rm=T) 
max_dist <- max(data$`DISTANCE (LIGHTYEARS)`, na.rm=T)

# Temperature 
min_temp <- min(data$`effective temperature`, na.rm=T)
max_temp <- max(data$`effective temperature`, na.rm=T) 

# Mass 
min_mass <- min(data$MASS, na.rm=T)
max_mass <- max(data$MASS, na.rm=T) 

# Radius 
min_rad <- min(data$`STAR RADIUS`, na.rm=T) 
max_rad <- max(data$`STAR RADIUS`, na.rm=T) 

# Luminosity 
min_lum <- min(data$Luminosity, na.rm=T) 
max_lum <- max(data$Luminosity, na.rm=T)


q6_table <- data.frame(
  Variable = c("Distance", "Temperature", "Mass", "Radius", "Luminosity"),
  Minimum = c(min_dist, min_temp, min_mass, min_rad, min_lum),
  Maximum = c(max_dist, max_temp, max_mass, max_rad, max_lum)
)

knitr::kable((q6_table), "simple") 
```




